5. A tutorial for `my_rf_cv`
  * Predict `body_mass_g` using covariates `bill_length_mm`, `bill_depth_mm`, and `flipper_length_mm`. 
  * Iterate through `k` in  `c(2, 5, 10)`:
    * For each value of `k`, run your function $30$ times. 
    * For each of the $30$ iterations,. store the CV estimated MSE.
  * Use `ggplot2` with 3 boxplots to display these data in an informative way. There should be a boxplot associated with each value of `k`, representing $30$ simulations each.
  * Use a table to display the average CV estimate and the standard deviation of the CV estimates across $k$. Your table should have 3 rows (one for each value of $k$) and 2 columns (one for the mean and the other for the standard deviation).
  * Discuss the results you observe in the boxplots and table. Compare the means and standard deviations of the the different values of $k$ and comment on why you think this is the case.
  
```{r}

# use load() and source() to call data 
load("../data/my_penguins.rda")
source("../Code/my_rf_cv.R")
```

```{r}
# create an empty matrix to hold MSE values
my_matrix <- matrix(NA, 90, 1)
# use for loop to run 30 iterations
for(i in 1 : 30) {
  # run function using k=2
  my_matrix[i, 1] <- my_rf_cv(2)
  # run function using k=5
  my_matrix[30+i, 1] <- my_rf_cv(5)
  # run function using k=2
  my_matrix[60+i, 1] <- my_rf_cv(10)
}

# calculate the mean and sd of the 30 simulations in k=2
mse2_mean <- mean(my_matrix[1 : 30, 1])
mse2_sd <- sd(my_matrix[1 : 30, 1])
# calculate the mean and sd of the 30 simulations in k=5
mse5_mean <- mean(my_matrix[31 : 60, 1])
mse5_sd <- sd(my_matrix[31 : 60, 1])
# calculate the mean and sd of the 30 simulations in k=10
mse10_mean <- mean(my_matrix[61 : 90, 1])
mse10_sd <- sd(my_matrix[61 : 90, 1])

# build a k input matrix as the index for my_matrix
k_matrix <- matrix(NA, 90, 1)
for(i in 1:30) {
  k_matrix[i, 1] <- "k = 2"
  k_matrix[30 + i, ] <- "k = 5"
  k_matrix[60 + i, ] <- "k = 10"
}

# create data frame to hold corresponding k value with cv_err
my_data <- data.frame(k_value = k_matrix[, 1], 
                      cv_err = my_matrix[, 1])

# create 3 boxplots with a boxplot associated with each value of k
my_boxplot <- ggplot(my_data, 
  aes(x = reorder(k_value, cv_err), y = cv_err)) + 
  geom_boxplot(fill = "light yellow") + 
  labs(title = "Cross validation error in k-alue equals 2, 5, and 10") +
  theme_bw(base_size = 12) +
  theme(plot.title = element_text(hjust = 0.5,
                                  face = "bold",
                                  size = 12)) + 
  xlab("k fold value") +
  ylab("Cross Validation Error")

# display boxplot
my_boxplot
```

```{r}
# create a table to display the average CV estimate and the standard deviation 
# of the CV estimates across k
my_table <- matrix(c(mse2_mean, mse2_sd, mse5_mean, mse5_sd, mse10_mean, 
                     mse10_sd), ncol = 2, byrow = TRUE)
# add row name for my_table
rownames(my_table) <- c("k = 2", "k = 5", "k = 10")
# add column name for my_table
colnames(my_table) <- c("mean", "sd")
# convert the matrix to a table and display the table
my_table <- as.table(my_table)
my_table
```

Saving my outputs:
```{r}
# same my_boxplot into Output/Figures
ggsave(filename = "rf_cv_boxplots.png", 
       plot = my_boxplot, 
       path = "../Output/Figures")

# save my_table into Output/Results
write.csv(my_table, file = "../Output/Results/rf_cv_table.csv")
```
